ManyPrimates-2021

### 2025-01-08 doc/charting/Bush-2022.qmd

@@

-   Github - open-source code, version control, collaboration -
    analysing
-   Python - open-source programming - analysing
-   R - open-source programming - analysing
-   arXiv/bioRxiv/psyRxiv - preprint sharing - disseminating
-   OpenNeuro - data sharing - disseminating
-   Open Science Framework - preregistration - planning
-   clinicaltrials.gov - preregistration - planning

>>>>

## Characteristics of the paper

-   Type of paper (e.g., tips, example): example
-   Themes (e.g., tools, organization): tools, workflow
-   Other keywords (e.g., newcomers):

@@

-   Github - open-source code, version control, collaboration -
    analysing
-   Python - open-source programming - analysing
-   R - open-source programming - analysing
-   arXiv/bioRxiv/psyRxiv - preprint sharing - disseminating
-   OpenNeuro - data sharing - disseminating
-   Open Science Framework - preregistration - planning
-   clinicaltrials.gov - preregistration - planning
-   FAIR (findability", "accessibility", "interoperability", and
    "reusability") -principles to organize data, not a tool per se, but
    I think they need to be emphasized - data collection, organization
    and sharing -
-   Brain imaging data structure (BIDS) - a common and standardized
    framework all scientists can work on - data collection and sharing
-   Containarized pipelines - code that allows easy reproduction - data
    analysis
-   ReproBIDS - dictionary with standardized terms for BIDS neuro data -
    planning, data collection, data deposition

### 2025-01-08 doc/charting/ManyPrimates-2019.qmd

---
title: ManyPrimates-2019
---

@@

-   Type of paper (e.g., tips, example): review?, example
-   Themes (e.g., tools, organization):
    -   organization
    -   tools
    -   review
-   Other keywords (e.g., newcomers):
    -   Systematic review
    -   Large-scale collaboration
    -   Large-scale infrastructure

>>>>

---
title: 'ManyPrimates-2019'
---

@@

-   Type of paper (e.g., tips, example): review?, example
-   Themes (e.g., tools, organization):
    -   organization
    -   tools
    -   review
    -   workflow
-   Other keywords (e.g., newcomers):
    -   Systematic review
    -   Large-scale collaboration
    -   Large-scale infrastructure

### 2025-01-08 doc/charting/ManyPrimates-2021.qmd

# Collaborative open science as a way to reproducibility and new insights in primate cognition research

@@

>>>>

# Collaboration and Open Science Initiatives in Primate Research

@@

## Characteristics of the paper

-   Type of paper (e.g., tips, example): example
-   Themes (e.g., tools, organization): organization, tools
-   Other keywords (e.g., newcomers):
